\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{\articletitle}

### 2016-04-07 paper/paper.tex
updated graphs and added correct figures

This paper will describe both algorithms, give the calculations for the asymptotic worst-case time complexity, as well as an examination of the computational results.
%------------------------------------------------
\section{Methods}
\label{methods}
%% WIP %%
The time complexity of both algorithms was calculated by hand. To verify the results, a computational experiment was performed. In this experiment, both algorithms were tested with various sizes of a graph consisting of three paths. The paths are connected to each other on both of their ends. In the experiment the only thing changing is the length of these paths.

@@

%------------------------------------------------
\section{Algorithms}
\label{algs}
%% TODO %%
% Describe algorithms, show concise calculations of time complexity
%%
For the paper, two different color refinement methods were implemented. The basic one gives all vertices in a graph with the same color but differently colored neighborhoods a separate color. This is done iteratively until the graph is stably colored. A coloring $\alpha$ of $G$ is stable if for all $u, v \in V(G)$ it holds that: if $\alpha(u) = \alpha(v)$, then $u$ and $v$ have identically colored neighborhoods. The problem with this method is that all vertices are checked each iteration.

@@

%------------------------------------------------
\section{Results}
\label{results}
%% TODO %%
% Give and describe results
%%
% Table for results can be found at appendices
The measured computation times are visualized in \autoref{fig:measurements}, the actual times can be found in \autoref{table:measurements}.

\begin{figure}[H]
	\includegraphics[width=\linewidth]{measurementsOnly}
	\caption{The computation times of both the basic and fast color refinement algorithms for various sizes of the three paths graph.}
	\label{fig:measurements}
\end{figure}

@@

\begin{figure}[H]
	\includegraphics[width=\linewidth]{measurementsOnly}
	\caption{The relative growth of measured computation time of the basic algorithm compared to the functions $f(x)=x^2$ and $f(x)=x^3$.}
	\label{fig:basicGrowth}
\end{figure}

\begin{figure}[H]
	\includegraphics[width=\linewidth]{measurementsOnly}
	\caption{The relative growth of measured computation time of the fast algorithm compared to the functions $f(x)=x^2$ and $f(x)=n\cdot log(n)$.}
	\label{fig:fastGrowth}
\end{figure}

@@

%------------------------------------------------
\section{Tables} %Change section name
\label{app:tab}
%% TODO %%
% Fill table with actual values
%%
%% NOTE %%
% All current values are fictional values for testing purposes only
%%
\begin{table}[h]\centering
\begin{tabular}{|l|r@{.}l|r@{.}l|}
\hline
Graph	
	& \multicolumn{2}{l|}{Basic \emph{(s)}}
	& \multicolumn{2}{l|}{Fast \emph{(s)}} \\
\hline
threepaths\_{}5
	& 0 & 00045
	& 0	& 0 \\
threepaths\_{}10
	& 0 & 0017
	& 0	& 0 \\
threepaths\_{}20
	& 0 & 0072
	& 0	& 0 \\
threepaths\_{}40
	& 0 & 031
	& 0	& 0 \\
threepaths\_{}80
	& 0 & 126
	& 0	& 0 \\
threepaths\_{}160
	& 0 & 604
	& 0	& 0 \\
threepaths\_{}320
	& 3 & 213
	& 0	& 0 \\
threepaths\_{}640
	& 19 & 261
	& 0	& 0 \\
threepaths\_{}1280
	& 127 & 567
	& 0	& 0 \\
threepaths\_{}2560
	& 907 & 407
	& 0	& 0 \\
threepaths\_{}5120
	& 5736 & 550
	& 0	& 0 \\
threepaths\_{}10240
	& \multicolumn{2}{c|}{-}
	& 0	& 0 \\

>>>>

This paper will describe both algorithms, give the calculations for the asymptotic worst-case time complexity, as well as an examination of the computational results.
%------------------------------------------------
\section{Methods}
\label{methods}
The time complexity of both algorithms was calculated by hand. To verify the results, a computational experiment was performed. In this experiment, both algorithms were tested with various sizes of a graph consisting of three paths. The paths are connected to each other on both of their ends. In the experiment the only thing changing is the length of these paths.

@@

%------------------------------------------------
\section{Algorithms}
\label{algs}
%% WIP %%
% Describe algorithms, show concise calculations of time complexity
%%
For the paper, two different color refinement methods were implemented. The basic one gives all vertices in a graph with the same color but differently colored neighborhoods a separate color. This is done iteratively until the graph is stably colored. A coloring $\alpha$ of $G$ is stable if for all $u, v \in V(G)$ it holds that: if $\alpha(u) = \alpha(v)$, then $u$ and $v$ have identically colored neighborhoods. The problem with this method is that all vertices are checked each iteration.

@@

%------------------------------------------------
\section{Results}
\label{results}
%% TODO %%
% Give and describe results
%%
% Table for results can be found at appendices
The measured computation times are visualized in \autoref{fig:basiconly} and \autoref{fig:fastonly}, the actual times can be found in \autoref{table:measurements}.

\begin{figure}[H]
	\includegraphics[width=\linewidth]{basiconly}
	\caption{The computation times of the basic color refinement algorithm for various sizes of the three paths graph.}
	\label{fig:basiconly}
\end{figure}

\begin{figure}[H]
	\includegraphics[width=\linewidth]{fastonly}
	\caption{The computation times of the fast color refinement algorithm for various sizes of the three paths graph.}
	\label{fig:fastonly}
\end{figure}

@@

\begin{figure}[H]
	\includegraphics[width=\linewidth]{basicfunctions}
	\caption{The computation times of the basic color refinement algorithm and the functions $f(n)=n^2$ and $f(n)=n^3$.}
	\label{fig:basicfunctions}
\end{figure}

\begin{figure}[H]
	\includegraphics[width=\linewidth]{basicdiff}
	\caption{The relative growth of measured computation time of the basic algorithm compared to the functions $f(n)=n^2$ and $f(n)=n^3$.}
	\label{fig:basicgrowth}
\end{figure}

\begin{figure}[H]
	\includegraphics[width=\linewidth]{fastfunctions}
	\caption{The computation times of the fast color refinement algorithm and the functions $f(x)=n\cdot log(n)$ and $f(x)=n$.}
	\label{fig:fastgrowth}
\end{figure}

\begin{figure}[H]
	\includegraphics[width=\linewidth]{fastdiff}
	\caption{The relative growth of measured computation time of the fast algorithm compared to the functions $f(x)=n\cdot log(n)$ and $f(x)=n$.}
	\label{fig:fastfunctions}
\end{figure}

@@

%------------------------------------------------
\section{Tables} %Change section name
\label{app:tab}
%% TODO %%
% Fill table with actual values
%%
%% NOTE %%
% All current values are fictional values for testing purposes only
%%
\begin{table}[h]\centering
\begin{tabular}{|l|r@{.}l|r@{.}l|}
\hline
Graph	
	& \multicolumn{2}{l|}{Basic \emph{(s)}}
	& \multicolumn{2}{l|}{Fast \emph{(s)}} \\
\hline
threepaths\_{}5
	& 0 & 00045
	& 0	& 00059 \\
threepaths\_{}10
	& 0 & 0017
	& 0	& 00086 \\
threepaths\_{}20
	& 0 & 0072
	& 0	& 0018 \\
threepaths\_{}40
	& 0 & 031
	& 0	& 0044 \\
threepaths\_{}80
	& 0 & 126
	& 0	& 0071 \\
threepaths\_{}160
	& 0 & 604
	& 0	& 014 \\
threepaths\_{}320
	& 3 & 213
	& 0	& 029 \\
threepaths\_{}640
	& 19 & 261
	& 0	& 058 \\
threepaths\_{}1280
	& 127 & 567
	& 0	& 117 \\
threepaths\_{}2560
	& 907 & 407
	& 0	& 261 \\
threepaths\_{}5120
	& 5736 & 550
	& 0	& 491 \\
threepaths\_{}10240
	& \multicolumn{2}{c|}{-}
	& 0	& 994 \\
threepaths\_{}10240
	& \multicolumn{2}{c|}{-}
	& 2	& 089 \\
